A Detailed Analysis of Performance Bottlenecks in MRI Pre-Processing

### 2023-11-30 paper/paper.tex
latest results.

\section{Methods}
\subsection{Infrastructure}
For our experiments, we used the \textit{Slashbin cluster} at Concordia University. The cluster has eight compute nodes, each configured with two 16-core Intel(R) Xeon(R) Gold 6130 CPU @ \SI{2.10}{\giga\hertz}, \SI{250}{\gibi\byte} of RAM, \SI{126}{\gibi\byte} of tmpfs, six \SI{447}{\gibi\byte} SSDs with the XFS file system (no RAID enabled), CentOS~8.1 and Linux kernel \textit{4.18.0-240.1.1.el8\_lustre.x86\_64}.

>>>>

\section{Methods}
\subsection{Infrastructure}
For our experiments, we used the \textit{Slashbin cluster} at Concordia University. The cluster has eight compute nodes, each configured with two 16-core Intel(R) Xeon(R) Gold 6130 CPU @ \SI{2.10}{\giga\hertz}, \SI{250}{\gibi\byte} of RAM, \SI{126}{\gibi\byte} of tmpfs, six \SI{447}{\gibi\byte} SSDs with the XFS file system (no RAID enabled), CentOS~8.1 and Linux kernel \textit{4.18.0-477.10.1.el8\_lustre.x86\_64}.
